\textbf{The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits}

### 2023-10-15 paper/1_Initial/manuscript.Rmd
minor

---
title             : "**The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits**"
shorttitle        : "PHQ-4R"
author:
  - name          : "Dominique Makowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
    email         : "dom.makowski@gmail.com"
    orcid         : 0000-0001-5375-9967
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Funding acquisition"
      - "Investigation"
      - "Methodology"
      - "Project administration"
      - "Resources"
      - "Software"
      - "Supervision"
      - "Validation"
      - "Visualization"
      - "Writing – original draft"
  - name          : "An Shu Te"
    affiliation   : "2"
    orcid         : 0000-0001-8008-2824
    role:
      - "Project administration"
      - "Resources"
      - "Software"
      - "Investigation"
      - "Writing – original draft"
  - name          : "S.H. Annabel Chen"
    affiliation   : "2, 3, 4, 5"
    orcid         : 0000-0002-1540-5516
    role:
      - "Project administration"
      - "Supervision"
      - "Writing – review & editing"
affiliation:
  - id            : "1"
    institution   : "School of Psychology, University of Sussex, UK"
  - id            : "2"
    institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
  - id            : "3"
    institution   : "LKC Medicine, Nanyang Technological University, Singapore"
  - id            : "4"
    institution   : "National Institute of Education, Singapore"
  - id            : "5"
    institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
abstract: |
  Something something.

@@

The purpose of this work is to re-analyze the factor structure of the scale using complementary statistical approaches, a further extend its validation by comparing a revised version with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*), as well as other relevant indices (such as psychopathological traits).

# Study 1

Study 1 is a re-analysis of the data from @murphy2020testing regarding the factor structure of the Interoceptive Accuracy Scale (IAS). The aim is to use a finer-grained method for estimating the optimal number of latent factors [namely, the *Method Agreement Procedure*, in @ludecke2020extracting; @makowski2018psycho], and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).

@@

The *Method Agreement Procedure* suggested 1 latent factor as optimal, supported by 5 (31.25%) out of 16 methods (Bentler, Acceleration factor, Scree (R2), VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).

@@

Finally, we re-fitted the CFA models on a new data set [study 6 of @murphy2020testing], which confirmed that the 5-factor balanced model had the better fit relative to the other models ($BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265$). However, the final model had poor to barely acceptable absolute indices of fit in both samples (Sample 1: $RMSEA = .067$ (acceptable < .08), $CFI = .878$ (acceptable > .9), $SRMR = .057$ (acceptable < .08); Sample 2: $RMSEA = .068$, $CFI = .906$, $SRMR = .063$).

@@

# Study 2

@@

One of the most intriguing new results was the reilationship between interoceptive abilities and several specific primal world beliefs.

>>>>

---
title             : "**The Revised Interoceptive Accuracy Scale (IAS-R) Confirms Links between Interoception and Personality and Psychopathological Traits**"
shorttitle        : "IAS-R"
author:
  - name          : "Dominique Makowski"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "HSS 04-18, 48 Nanyang Avenue, Singapore"
    email         : "dom.makowski@gmail.com"
    orcid         : 0000-0001-5375-9967
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - "Conceptualization"
      - "Data curation"
      - "Formal Analysis"
      - "Funding acquisition"
      - "Investigation"
      - "Methodology"
      - "Project administration"
      - "Resources"
      - "Software"
      - "Supervision"
      - "Validation"
      - "Visualization"
      - "Writing – original draft"
  - name          : "An Shu Te"
    affiliation   : "2"
    orcid         : 0000-0001-8008-2824
    role:
      - "Project administration"
      - "Resources"
      - "Software"
      - "Investigation"
      - "Writing – original draft"
  - name          : "S.H. Annabel Chen"
    affiliation   : "2, 3, 4, 5"
    orcid         : 0000-0002-1540-5516
    role:
      - "Project administration"
      - "Supervision"
      - "Writing – review & editing"
affiliation:
  - id            : "1"
    institution   : "School of Psychology, University of Sussex, UK"
  - id            : "2"
    institution   : "School of Social Sciences, Nanyang Technological University, Singapore"
  - id            : "3"
    institution   : "LKC Medicine, Nanyang Technological University, Singapore"
  - id            : "4"
    institution   : "National Institute of Education, Singapore"
  - id            : "5"
    institution   : "Centre for Research and Development in Learning, Nanyang Technological University, Singapore"
abstract: |
  Something something.

@@

The purpose of this work is to reanalyse the factor structure of the scale using complementary statistical approaches, a further extend its validation by comparing a revised version with one of the most popular questionnaire of interoception, the MAIA-2 (*ref*), as well as other relevant indices (such as psychopathological traits).

# Study 1 - Reanalysis of Murphy et al. (2020)

Study 1 is a reanalysis of the data from @murphy2020testing regarding the factor structure of the Interoceptive Accuracy Scale (IAS). The aim is to use a more fine-grained method for estimating the optimal number of latent factors [namely, the *Method Agreement Procedure*, in @ludecke2020extracting; @makowski2018psycho], and perform a statistical model comparison using Confirmatory Factor Analysis (CFA).

@@

The *Method Agreement Procedure* suggested 1 latent factor as optimal, supported by 5 (31.25%) out of 16 methods (Bentler, Acceleration factor, Scree - R2, VSS complexity 1, Velicer's MAP), followed by 4 factors supported by 4 methods (Kaiser criterion, beta score, optimal coordinates, parallel analysis).

@@

Finally, we re-fitted the CFA models on a new dataset [sample 2, from study 6 of @murphy2020testing], which confirmed that the 5-factor balanced model had the better fit relative to the other models ($BIC_{CFA-5mod} = 17316; BIC_{CFA-5h} = 17323; BIC_{CFA-5} = 18257; BIC_{EFA-4mod} = 18265$). However, the final model had poor to barely acceptable absolute indices of fit in both samples (Sample 1: $RMSEA = .067$ (acceptable < .08), $CFI = .878$ (acceptable > .9), $SRMR = .057$ (acceptable < .08); Sample 2: $RMSEA = .068$, $CFI = .906$, $SRMR = .063$).

@@

# Study 2 - Online validation of new structure

@@

<!-- One of the most intriguing new results was the relationship between interoceptive abilities and several specific primal world beliefs. -->
